The Neuro Bureau ADHD-200 Preprocessed Repository

### 2016-05-22 Bellec_ADHD200_2016.tex
Bug fix in URL reference.

The impact of the ADHD-200 Preprocessed repository demonstrated the need for reducing computational barriers to participation in discovery neuroscience, including but not limited to machine learning competitions based on neuroimaging data. The ADHD-200 Preprocessed release has contributed and will continue to contribute to respond to that need. We still believe that a much larger-scale effort will be necessary to unlock the full potential of openly shared neuroimaging data in the service of accelerating neuroimaging research. In line with the grassroots, open science ethos of the Neurobureau, new contributors interested in sharing derivatives of ADHD-200 or other open imaging data repository can contact us via a forum\footnote{http://www.nitrc.org/forum/?group_id=383}. We are also actively seeking for contributions, notably during brainhack events\citep{Craddock2016}. An important current project is the ABIDE preprocessed initiative\footnote{\url{http://preprocessed-connectomes-project.org/abide/}} \citep{dimartino2014}. This new resource, still under development, will include over 15 different processing strategies for rs-fMRI processing, implemented across 4 different software packages, and 2 different pipelines for structural MRI processing. The release will feature an harmonized organization of processed derivatives across packages and extensive quality control. We are planning to continue to expand this line on work on other data sources in the near future. Our hope is that ADHD-200 Preprocessed and future related efforts will critically help fMRI researchers to identify optimal analytical paths for a given task.

>>>>

The impact of the ADHD-200 Preprocessed repository demonstrated the need for reducing computational barriers to participation in discovery neuroscience, including but not limited to machine learning competitions based on neuroimaging data. The ADHD-200 Preprocessed release has contributed and will continue to contribute to respond to that need. We still believe that a much larger-scale effort will be necessary to unlock the full potential of openly shared neuroimaging data in the service of accelerating neuroimaging research. In line with the grassroots, open science ethos of the Neurobureau, new contributors interested in sharing derivatives of ADHD-200 or other open imaging data repository can contact us via a forum\footnote{\url{http://www.nitrc.org/forum/?group_id=383}}. We are also actively seeking for contributions, notably during brainhack events\citep{Craddock2016}. An important current project is the ABIDE preprocessed initiative\footnote{\url{http://preprocessed-connectomes-project.org/abide/}} \citep{dimartino2014}. This new resource, still under development, will include over 15 different processing strategies for rs-fMRI processing, implemented across 4 different software packages, and 2 different pipelines for structural MRI processing. The release will feature an harmonized organization of processed derivatives across packages and extensive quality control. We are planning to continue to expand this line on work on other data sources in the near future. Our hope is that ADHD-200 Preprocessed and future related efforts will critically help fMRI researchers to identify optimal analytical paths for a given task.
